\newenvironment{acknowledgementpage}[1]{
\newpage
\begin{center}
    \large \textbf{ACKNOWLEDGEMENT}
\end{center}

\vspace{2ex}

First of all, I express my gratitude to the Almighty, who blessed me with the zeal and enthusiasm to complete this research work successfully. I am extremely thankful to my supervisors' Dr. Bhaskar Mondal, Assistant Professor, Computer Science and Engineering Department, National Institute of Technology Patna, Patna for their motivation and tireless efforts to help me to get deep knowledge of the research area and for supporting me throughout the life cycle of my B. Tech. dissertation work. Especially, the extensive comments, healthy discussions, and fruitful interactions with the supervisors had a direct impact on the final form and quality of B. Tech. dissertation work. \\

I am also thankful to the Name of The Dr. M. P. Singh, Head of the Computer Science and Engineering Department, for his fruitful guidance through the early years of chaos and confusion. I wish to thank the faculty members and supporting staff of the Computer Science and Engineering Department for their full support and heartiest cooperation. \\

This thesis would not have been possible without the hearty support of my friends. My deepest regards to my Parents for their blessings, affection, and continuous support. Also, Last but not least, I thank GOD, the almighty for giving me the inner willingness, strength, and wisdom to carry out this research work successfully. 

\hfill #1
}{}
